The problem and promise of scale in multilayer animal social networks

### 2020-02-11 paper/manuscript.Rmd
add todo
reorg, edits social scale results

<!-- TODO: units of spatial scale? -->

@@

<!-- TODO: discuss layer similarity for social threshold -->
In general, individuals in multilayer networks became more connected as social
scale increased; however, this relationship varied by habitat type and season.
As social scale increased, connective redundancy increased rapidly when groups
were formed up to approximately 100 m threshold, followed by a plateau and
slight decrease at higher thresholds, presumably due to an increase in summer
forest degree at ~500 m (Figure \@ref(fig:socres)d). Regardless of social scale,
layer relevance did not change for any habitat types or seasons, which suggests
habitat-by-season layers captured most, if not all, of the potential connections
an individual would have across all networks (Figure \@ref(fig:socres)b).
Finally, somewhat predictably, graph strength for winter networks increased up
to ~100-200 m thresholds, followed by a plateau, while graph strength for summer
networks did not change as the social threshold increased (Figure
\@ref(fig:socres)a).  Taken together, these results suggest the optimal social
scale at which groups should be assigned is likely somewhere between ~20-100 m
based on the rate at which network metrics stabilized. For ungulates, groups are
often assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018;
Peignier et al. 2019), suggesting that given similar quantities of data, ~50 m
is likely an ideal social scale for generating social networks in caribou and
similar species.

>>>>

<!-- TODO: units of spatial scale? --> 
<!-- TODO: citations? -->

@@

<!-- TODO: discuss layer similarity for social threshold -->
In general, individuals in multilayer networks became more connected as social
scale increased; however, this relationship varied by habitat type and season.
As social scale increased, graph strength for winter networks increased to
~100-200 m thresholds, followed by a plateau, while graph strength for summer
networks did not change as the social threshold increased (Figure
\@ref(fig:socres)a). Layer relevance increased for winter networks between 5 and
50 m social thresholds, then did not change for any habitat types which suggests
the winter habitat layers captured most, if not all, of the potential
connections an individual would have across all networks (Figure
\@ref(fig:socres)b). <!-- missing summer--> Connective redundancy increased
rapidly when groups were formed up to approximately 100 m threshold, followed by
a plateau and slight decrease at higher thresholds, presumably due to an
increase in summer forest degree at ~500 m (Figure \@ref(fig:socres)d). Taken
together, these results suggest the optimal social scale at which groups should
be assigned is likely somewhere between ~20-100 m based on the rate at which
network metrics stabilized. For ungulates, groups are often assigned based on 50
m threshold (Lingle 2003; Lesmeries et al. 2018; Peignier et al. 2019),
suggesting that given similar quantities of data, ~50 m is likely an ideal
social scale for generating social networks in caribou and similar species.
